---
title: "Parp1 Specificity"
author: "Robert M Flight"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Parp1 Specificity}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

There has been some question about whether the signal observed in this data set is Parp1 specific or general nucleosome binding. This vignette attempts to answer that question using the histone modification marks as indicators of general nucleosome binding in the matched cell types, and compared to the Parp1 associated nucleosomes.

## Proposed Analysis

* Tile genome into equally sized tiles
* Define cutoff of signal to denote *presence* of nucleosomes
* Using *all* histone marks as indicators of *general* nucleosome binding, find tiles **with** nucleosome binding
* Using *parp1* reads, find tiles **with** parp1 associated nucleosomes
* Sample 1000 random tiles, count *general* and *parp1* nucleosomes
* Repeat 1000 times
* Compare distributions of *general* and *parp1* counts

## Load Data

```{r load_data, message=FALSE}
library(ggplot2)
library(GenomicFiles)
library(BSgenome.Hsapiens.UCSC.hg19)
library(fmcorrelationbreastcaparp1)
library(fmdatabreastcaparp1)
data("histone_marks") # mcf-7 histone modifications
data("parp1_ln4_unique") # mcf-7 parp1 reads
```

## Tile Genome & Coverage

```{r tile}
genome_tiles <- tileGenome(seqinfo(Hsapiens), tilewidth = 500, cut.last.tile.in.chrom = TRUE)
```

```{r parp1_counts}
min_sum <- 25
parp1_cov <- coverage(parp1_ln4_unique, weight = "n_count")
genome_tiles <- binned_function(genome_tiles, parp1_cov, "sum", "parp1")
mcols(genome_tiles)$parp1[mcols(genome_tiles)$parp1 < min_sum] <- 0
mcols(genome_tiles)$parp1[mcols(genome_tiles)$parp1 >= min_sum] <- 1
```

```{r nucleosome_counts}
mcols(genome_tiles)$histmod <- 0
histone_tiles <- genome_tiles
for (i_name in names(histone_marks)){
  histone_cov <- coverage(histone_marks[[i_name]], weight = "mcols.signal")
  histone_tiles <- binned_function(histone_tiles, histone_cov, "sum", i_name)
  mcols(genome_tiles)$histmod[mcols(histone_tiles)[, i_name] > 0] <- 1 
}
```

## Sample & Count

Now we will take a bunch of samplings from the tiles, and then count how many have **nucleosomes** and how many have **parp1**.

```{r sample}
n_sample <- 1000
out_counts <- lapply(seq(1, 1000), function(x){
  use_loc <- sample(length(genome_tiles), n_sample)
  tmp <- colSums(as.matrix(mcols(genome_tiles[use_loc])))
  data.frame(counts = tmp, which = names(tmp))
})
out_counts <- do.call(rbind, out_counts)
```

## Plot!

```{r plotit}
ggplot(out_counts, aes(x = counts, fill = which)) + geom_histogram(alpha = 0.8, binwidth = 1, position = "identity")
```

## Genome Wide Patterns

How many tiles have only Parp1 binding (expect few), *vs* how many have both (expect majority of Parp1), *vs* how many have nucleosome only?

```{r count_specificity}
presence <- mcols(genome_tiles)
parp_only <- sum(as.logical(presence$parp1) & !as.logical(presence$histmod))
histmod_only <- sum(!as.logical(presence$parp1) & as.logical(presence$histmod))
both <- sum(as.logical(presence$parp1) & as.logical(presence$histmod))
```

* Parp only: `r parp_only`
* histone modification only: `r histmod_only`
* both: `r both`

## MNase Nucleosome Signal

Have downloaded the MNase nucleosome signal from ENCODE for GM12878 and K562. Will combine these to generate overall nucleosome signal.

```{r load_nuc_signal, eval = FALSE}
genome_tiles <- genome_tiles[seqnames(genome_tiles) %in% seqnames(seqinfo(BigWigFile("../wgEncodeSydhNsomeGm12878Sig.bigWig")))]
seqlevels(genome_tiles) <- paste0("chr", c(seq(1, 22), "X", "M"))

#tmp_tiles <- genome_tiles[sample(length(genome_tiles), 1000)]

MAP <- function(RANGE, FILE, ...) {
  tmp <- import.bw(FILE, selection=RANGE, as="GRanges")
  unlist(sum(runValue(coverage(tmp, weight = "score")[RANGE])))
}

bw_counts <- reduceByRange(genome_tiles, files = "../wgEncodeSydhNsomeGm12878Sig.bigWig", MAP)
bw_counts2 <- unlist(bw_counts)
```

